---
title: "RDM homework - Analysis report"
author: "Helene Langet"
format: docx
editor: visual
---

```{r}
# Load required libraries

# Load the tidyverse collection of packages for data manipulation and visualization
library(tidyverse)

# Load the haven package to read and work with Stata, SPSS, and SAS data files
library(haven)

# Load the gtsummary package to create publication-ready summary tables
# Useful for descriptive statistics and model result tables with clean formatting
library(gtsummary)
```

```{r}
# Load the (clean) household-level data 
household_df <- haven::read_dta("../data/cleanR_household_with_village.dta")

# Load the (clean) household-level data 
# ...
```
# About the National Malaria Indicator Survey 2019/2020

Cross-sectional household survey in all 22 provinces of Papua New Guinea.

* 5 randomly sampled villages/province
* ca. 30 random households/village
* Structured interviews
* Finger-prick blood sample for malaria diagnosis by Rapid Diagnostic Test (RDT) and light microscopy

# Shell tables

## Shell 1

## Shell 2

```{r}
household_df |>
  dplyr::select(altitude) |>
  gtsummary::tbl_summary(label = list("altitude" ~ "Altitude (m)"))
```

## Shell 3

# Question 1

How many household interviews were conducted per month? 

```{r}
count_df <- household_df |>
  dplyr::group_by(month) |>
  dplyr::count()
count_df
```

Instructions:

* Step 1: Add color to bars
* Step 2: Add data labels to the bars
* Step 3: Adjust the y-axis limits
* Step 4: Improve x-axis date formatting
* Step 5: Add labels to the axes
* Step 6: Highlight year transitions with a vertical line
* Step 7: Apply a minimal theme
* Step 8: Customize theme elements for cleaner look
* Step 9: Add a caption
* Step 10: Adjust the dimensions of the figure so that its width is twice its height

```{r}
count_df |>
  ggplot(mapping = ggplot2::aes(x = month, y = n)) +
    ggplot2::geom_bar(stat = "identity")
```

# Question 2

Are members of households that own at least one long-lasting insecticidal net (LLIN) less likely to be infected with malaria parasites?

# Question 3

Does prevalence of Plasmodium vivax and P. falciparum differ between altitudinal zones?

# Question 4

What is the sensitivity and specificity of RDTs compared to microscopy (any species)?